Automated iterative near-term forecasting for the Portal Project

### 2018-02-08 manuscript/portal_iterative_forecasting_ms.Rmd
Edits to intro paragraph 2

With the goal of making ecological forecasting more dynamic and responsive, Dietze et al [-@dietze2018] recently called for an increase in iterative near-term forecasting. Iterative near-term forecasting is defined by making predictions for the near future and repeatedly updating those predictions through a cycle of evaluation, integration of new data, and generation of new forecasts. Because forecasts are made 'near-term'---daily to annual time scales instead of multi-decadal---predictions can be assessed more quickly and frequently, leading to more rapid model improvements [@tredennick2016; @dietze2018]. In addition, since forecasts are made repeatedly through time, new data can be continuosly integrated with each iteration [@dietze2018]. As a result, iterative near-term forecasting has the potential to promote rapid improvement in the state of ecological forecasting by quickly identifying how models are failing, facilitating rapid testing of improved models, and incorporating the most up-to-date data available. In addition to yielding improved information for guiding policy and management [@clark2001; @luo2011; @petchey2015], this iterative approach will help improve our basic understanding of ecological systems [@dietze2018]. For example, alternative mechanistic models can be compared to determine which model provides the best forecasts, thus providing insights into the importance of different ecological processes [@dietze2018]. Iterative near-term forecasting provides a more dynamic interplay between models, predictions, and data that will improve ecological forecasting and our understanding of ecological systems more broadly.

>>>>

With the goal of making ecological forecasting more dynamic and responsive, Dietze et al [-@dietze2018] recently called for an increase in iterative near-term forecasting. Iterative near-term forecasting is defined as making predictions for the near future and repeatedly updating those predictions through a cycle of evaluation, integration of new data, and generation of new forecasts. Because forecasts are made 'near-term'---daily to annual time scales instead of multi-decadal---predictions can be assessed more quickly and frequently, leading to more rapid model improvements [@tredennick2016; @dietze2018]. Since forecasts are made repeatedly through time, new data can be continuously integrated with each iteration [@dietze2018]. By quickly identifying how models are failing, facilitating rapid testing of improved models, and incorporating the most up-to-date data available, iterative near-term forecasting has the potential to promote rapid improvement in the state of ecological forecasting. In addition to yielding improved information for guiding policy and management [@clark2001; @luo2011; @petchey2015], this iterative approach will help improve our basic understanding of ecological systems [@dietze2018]. For example, alternative mechanistic models can be compared to determine which model provides the best forecasts, thus providing insights into the importance of different ecological processes [@dietze2018]. Iterative near-term forecasting provides the more dynamic interplay between models, predictions, and data that has been identified has necessary for improving ecological forecasting and our understanding of ecological systems more broadly.
